\newpage
\raggedright
\addcontentsline{toc}{section}{Список литературы}
\begin{thebibliography}{99}
\bibitem{boldewin06}
Boldewin F. The big SoftICE how-to [PDF] (\url{http://www.reconstructer.org/papers/The%20big%20SoftICE%20howto.pdf}).

\bibitem{dolgova08}
Dolgova K., Chernov A. Automatic Type Reconstruction in Disassembled C Programs // 15th Working Conference on Reverse Engineering. 2008. P. 202-206.

\bibitem{emmerik04}
Emmerik M. V., Waddington T. Using a Decompiler for Real-World Source Recovery // 11th Working Conference on Reverse Engineering. 2004. P. 27-36.

\bibitem{emmerik07}
Emmerik M. V. Static Single Assignment for Decompilation [PDF] (\url{http://vanemmerikfamily.com/mike/master.pdf}).
%A thesis submitted for the degree of Doctor of Philosophy at The University of Queensland, 2007.

\bibitem{gray94}
Gray J. C++: {\begin{CJK*}{UTF8}{ipam}水面下の仕組み\end{CJK*}} [HTML] (\url{http://www.microsoft.com/japan/msdn/vs_previous/visualc/techmat/feature/jangrayhood/}).
%Gray J. C++: Under the Hood [HTML] (\url{http://msdn.microsoft.com/archive/en-us/dnarvc/html/jangrayhood.asp}).

\bibitem{kochhar02}
Kochhar V. How a C++ compiler implements exception handling [HTML] (\url{http://www.codeproject.com/KB/cpp/exceptionhandler.aspx}).

\bibitem{mycroft99}
Mycroft A. Type-Based Decompilation // 8th European Symposium on Programming Languages and Systems. 1999. P. 208-223.

\bibitem{palmer94}
Palmer C., Kershenbaum A. Representing trees in genetic algorithms // First IEEE Conference on Evolutionary Computation. 1994. P. 27-29.

\bibitem{sabanal07}
Sabanal P., Yason M. Reversing C++ // Black Hat DC. 2007.

\bibitem{seonghoon06}
Seonghoon K. Microsoft C++ Name Mangling Scheme [HTML] (\url{http://mearie.org/documents/mscmangle}).

\bibitem{skochinsky06}
Skochinsky I. Reversing Microsoft Visual C++ Part II: Classes, Methods and RTTI [HTML] (\url{http://www.openrce.org/articles/full_view/23}).

\bibitem{stroustrup93}
Stroustrup B. A history of C++: 1979–1991 // The second ACM SIGPLAN conference on History of programming languages. 1993. P. 271-297.

\bibitem{stroustrup97}
Stroustrup B. The C++ programming language 3rd edition. Massachusetts: Addison-Wesley, 1997. 1022 p.

\bibitem{wiener05}
Wiener R. Obfuscation and .NET // Journal of Object Technology. 2005. 4. N 4. P. 73-92.

\bibitem{lippman07ru}
Липпман С., Му Б., Лажойе Ж. Язык программирования C++, вводный курс, 4-е издание. М.: Вильямс, 2007. 896 с.

\bibitem{stroustrup97ru}
Строуструп Б. Язык программирования С++, специальное издание. М.: Бином, 2004. 1104 с.

\bibitem{stroustrup90ru}
Эллис М., Строуструп Б. Справочное руководство по языку программирования С++ с комментариями. Проект стандарта ANSI. M.: Мир, 1992. 445 с.

\bibitem{abi}
Application Binary Interface [HTML] (\url{http://en.wikipedia.org/wiki/Application_binary_interface}).

\bibitem{boomerang}
Boomerang. BSD licensed software [HTML] (\url{http://boomerang.sourceforge.net/}).

\bibitem{graphviz}
GraphViz. CPL licensed software [HTML] (\url{http://www.graphviz.org/}).

\bibitem{softicescripting}
IceX. A free SoftICE Plugin [HTML] (\url{http://mamaich.uni.cc/}).

\bibitem{idapro}
IDA Pro Disassembler. Proprietary software [HTML] (\url{http://www.hex-rays.com/idapro/}).

\bibitem{idapython}
IDAPython. A free IDA Pro plugin [HTML] (\url{http://www.d-dome.net/idapython}).

\bibitem{idarub}
IDARub. A free IDA Pro plugin [HTML] (\url{http://www.metasploit.com/users/spoonm/idarub/}).

\bibitem{cpp03}
ISO/IEC Standard 14882:2003. Programming languages - C++. New York: American National Standards Institute, 2003. 786 p.

\bibitem{gccabi}
Itanium C++ ABI, revision 1.86 [HTML] (\url{http://www.codesourcery.com/public/cxx-abi/abi.html}).

\bibitem{mfc}
Microsoft Foundation Class Library Reference [HTML] (\url{http://msdn.microsoft.com/en-us/library/d06h2x6e.aspx}).

\bibitem{ollydbg}
OllyDbg. Proprietary software [HTML] (\url{http://www.ollydbg.de/}).

\bibitem{ollypython}
OllyPython. A free OllyDbg plugin [HTML] (\url{http://code.google.com/p/ollypython/}).

\bibitem{polymorphism}
Polymorphism in object-oriented programming [HTML] (\url{http://en.wikipedia.org/wiki/Polymorphism_in_object-oriented_programming}).

\bibitem{qt}
Qt --- A cross-platform application and UI framework [HTML] (\url{http://www.qtsoftware.com/products/}).

\bibitem{wine}
Wine. LGPL licensed software [HTML] (\url{http://www.winehq.org}).

\bibitem{idaproproc}
Поддерживаемые типы процессоров IDA Pro - Interactive Disassembler [HTML] (\url{http://www.idapro.ru/description/proc/}).

\bibitem{idaproformats}
Поддерживаемые форматы входных файлов IDA Pro - Interactive Disassembler [HTML] (\url{http://www.idapro.ru/description/format/}).

\end{thebibliography}






















